Bullet Groups as a test of $\Lambda$CDM

### 2014-03-04 paper/ms.tex
seeding paragraphs

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

@@

\subsection{Relative Velocities}
\label{fig:velocities}

@@

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
\end{center}
\caption{
Integrated probability distribution for the displacement
  between the host halo and its dominand sub-halo. The left panel
  shows the results in terms of the physical displacements and the
  right panel the same displacement normalized by the virial radius of
  the host halo. The continous line corrresponds to the halos in the
  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
  The vertical stripe corresponds to the estimate of the separation
  between the two dark matter clumps in the results reported by
  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
  shows the same results normalized by the virial radius of the host
  halo.} 
\label{fig:displacement}
\end{figure*}

@@

\subsection{Relative Velocities}
\label{sec:velocities}

\begin{figure*}
\begin{center}
%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
\end{center}
\caption{Integrated probability distribution for the relative velocity of the
sub-halo with respect to its host. The left panel shows the results
in physical units while the right panel show the same values
normalized by the circular velocity of the host halo. The line coding
follows the same structure as Figure \ref{fig:displacements}}
\label{fig:velocities}
\end{figure*}

In Figure \ref{fig:velocities} we present the integrated probability
of the relative peculiar velocities of the sub-halos with respect to
the host halo. The left panel presents this velocity in physical units
while the left panel presents them as a fraction of the circular
velocity of the host halo.

@@

In order to facilitate the reproducibility and reuse of our results we
have made available all the data and the source code available in a public
repository. [...]
